### 2025-09-17 paper/sec/authoring-workflow.tex
Simplify loopback description.

Expressions generated by the \InterpretationAgent are evaluated by the Fluid interpreter. If evaluation fails,
the error is used to extend the prompt and the extended prompt is sent back to the LLM for regeneration. This
loopback mechanism enables iterative refinement of expressions, improving accuracy and robustness. Three types
of errors are handled:

\begin{itemize}
    \item \textbf{Invalid Program}. Evaluation fails due a syntax error, undeclared identifer, division by
    zero, array index out of bounds or other runtime problem.
    \item \textbf{Invalid Expression Type}. The value of the expression is not a string.
    \item \textbf{Mismatching String}. The value of the expression is a string, but is not equal to
    highlighted target text.
\end{itemize}

>>>>

Expressions generated by the \InterpretationAgent are evaluated by the Fluid interpreter. If evaluation fails,
the error is used to extend the prompt and the extended prompt is sent back to the LLM for regeneration. This
loopback mechanism enables iterative refinement of expressions, improving accuracy and robustness. There are
two kinds of loopback error:

\begin{itemize}
    \item \textbf{Invalid Program}. Evaluation fails due a syntax error, undeclared identifier, division by
    zero, array index out of bounds or other runtime problem.
%    \item \textbf{Invalid Expression Type}. The value of the expression is not a string.
    \item \textbf{Mismatching String}. The string value of the expression is not equal to the target text.
\end{itemize}
